---
title: "exploratory_data analysis_project"
author: "Kasturi Bhatt"
date: "2024-11-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Testing different plots

Load packages
```{r}
library(dplyr)
library(tidyverse)
```

read data
```{r}
ffg_data <- read_csv("final_mean_proportion_by_ffg_and_site.csv")

ffg_data<- ffg_data%>%
  subset(ffg!="UN")%>%
  subset(ffg!="PI")
```

#data wrangling

##separating different rivers
```{r}
CLS_river <- ffg_data%>%
  subset(river=="CLS")

ELS_river <- ffg_data%>% 
  subset(river=="ELS")

RCLS_river <- ffg_data%>%
  subset(river=="RCLS")
```


#Exploratory plots

##River gradient vs count plots by ffg

###CLS river
```{r}
CLS_river%>% 
  group_by(ffg)%>%
  ggplot(aes(x=site, y=mean_proportion, colour=ffg))+
  geom_line()
```

###ELS river
```{r}
ELS_river%>% 
  group_by(ffg)%>%
  ggplot(aes(x=site, y=mean_proportion, colour=ffg))+
  geom_line()
```

###CLS river
```{r}
RCLS_river%>% 
  group_by(ffg)%>%
  ggplot(aes(x=site, y=mean_proportion, colour=ffg))+
  geom_line()
```



##Comparing Rivers

```{r}
ffg_data%>%
  group_by(ffg)%>%
  ggplot(aes(x=site, y=mean_proportion, colour=ffg))+
  geom_line()+
  facet_wrap(~river, scales = "free_x")
 
```

##Without CG CF

```{r}
ffg_data%>%
  group_by(ffg)%>%
  filter(ffg!="CF")%>%
  filter(ffg!="CG")%>%
  ggplot(aes(x=site, y=mean_proportion, colour=ffg))+
  geom_line()+
  facet_wrap(~river, scales = "free")
```


quick look at count data

```{r}
count_data<- read_csv("ffg_long_counts.csv")
```

```{r}
count_data%>%
  subset(ffg!="UN")%>%
  subset(river=="CLS")%>%
  group_by(ffg)%>%
  summarise(total_count=sum(count))
```


##Plots with combined feeding groups

```{r}
new_ffg_prop<- read_csv("new_ffg_prop.csv")
```

```{r}
new_ffg_prop%>%
  group_by(new_ffg)%>%
  ggplot(aes(x=site, y=mean_proportion, colour=new_ffg))+
  geom_line()+
  facet_wrap(~river, scales = "free_x")

#see that #of collectors highest at end, which makes sense acc to diagram
#also makes sense that collectors stays high in proportion than all others
```

remove C to look at rest

```{r}
new_ffg_prop%>%
  group_by(new_ffg)%>%
  subset(new_ffg!="C")%>%
  ggplot(aes(x=site, y=mean_proportion, colour=new_ffg))+
  geom_line()+
  facet_wrap(~river, scales = "free_x")
```

effect of site?? especially in CLS looks like certain sites just have more of all ffg
also see that SH high at beginnig which makes sense!! (clear in ELS)
predators everywhere, makes sense. inc where other things increase.
scrapers should generally inc. around middle, which we kind of see in CLS & ELS



